---
title: "Content"
---


The course content is divided in chapters: for each topic,
readers have access to course notes, sample code, online quizzes and exercises.

## Course notes

- [Basics of statistical inference](https://lbelzile.github.io/math60604a/intro.html)
- [Linear regression](https://lbelzile.github.io/math60604a/linear-regression.html)
- [Generalized linear models](https://lbelzile.github.io/math60604a/generalized-linear-models.html)
- [Correlated and longitudinal data](https://lbelzile.github.io/math60604a/correlated-longitudinal-data.html)
- [Linear mixed models](https://lbelzile.github.io/math60604a/linear-mixed-models.html)
- [Survival analysis](https://lbelzile.github.io/math60604a/survival.html)
- [Likelihood](https://lbelzile.github.io/math60604a/likelihood.html)



## Videos and Slides

In this section you can find the links to all videos individually as well as the slides and accompanying code used in the videos.

```{r, echo=FALSE, eval=TRUE, message=FALSE}
source("../files/get_slide_data.R")
knitr::kable(sldat, align = "llccccc")
```

---

## Data

The **SAS** databases (`.sas7bdat`) can be downloaded [by clicking on this link](https://raw.githubusercontent.com/lbelzile/statmod/main/datasets/MATH60604A_SAS_data.zip). Create a repository on SAS onDemand, add these files and create a library as shown in the Introduction to SAS.

To access the course database, you can also add the following code snippet in your **SAS** autoload:

`LIBNAME statmod "~/my_shared_file_links/u41148888/statmod" access=readonly;`

You must create a local copy to modify these data.

You can also access the data sets in **R** by installing the `hecstatmod` package from Github using the following commands (uncomment the first line to install the  `remotes` and `learnr` libraries - do only once):

```{r, eval = FALSE}
#install.packages(c("learnr","remotes"))
remotes::install_github("lbelzile/hecstatmod")
```
*Note*: not all data sets are currently documented and (most) tutorials are still missing. Please re-install the package periodically to benefit from the latest features.

## Quiz

The **R** package also contain quizzes: to run the later and launch a new browser window, use the following commands (each line represents a different quiz).

```{r eval = FALSE}
learnr::run_tutorial("intro", package = "hecstatmod")
learnr::run_tutorial("likelihood", package = "hecstatmod")
```

